---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# outscrapr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/CorradoLanera/outscrapr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/CorradoLanera/outscrapr?branch=main)
[![test-coverage](https://github.com/CorradoLanera/outscrapr/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/CorradoLanera/outscrapr/actions/workflows/test-coverage.yaml)
[![R-CMD-check](https://github.com/CorradoLanera/outscrapr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CorradoLanera/outscrapr/actions/workflows/R-CMD-check.yaml)
[![R-CMD-checkdev](https://github.com/CorradoLanera/outscrapr/actions/workflows/R-CMD-checkdev.yaml/badge.svg)](https://github.com/CorradoLanera/outscrapr/actions/workflows/R-CMD-checkdev.yaml)
<!-- badges: end -->

The goal of `{outscrapr}` is to implement a simplified subset of the [Outscraper](https://outscraper.com/) API in R.

## Installation

You can install the development version of `{outscrapr}` like so:

``` r
devtools::install_github("CorradoLanera/outscrapr")
```

## Places

### Single query
```{r}
library(outscrapr)

# Get your API key from https://outscraper.com/ and set it as the
# environment variable `OUTSCRAPER_API_KEY`
query <- "restaurants, Brooklyn 11203"

restaurants <- google_maps_search(query = query, limit = 2)

restaurants

restaurants$working_hours
restaurants$about
restaurants$about$`Popular for`
restaurants$reviews_per_score
```

### Multiple queries
You can retrieve max 500 places per one query search on Google Maps.
For densely populated areas you might want to split your query into
subqueries in order to get all the places inside.
(e.g., `c("restaurants, Brooklyn 11211", "restaurants, Brooklyn 11215")`).

```{r}
queries <- c(
  "restaurants, Brooklyn 11211",
  "restaurants, Brooklyn 11215"
)

# Results' limit refers to the number of places to retrieve for each
# query. The results of all queries are combined into a single tibble.
multi_restaurants <- google_maps_search(query = queries, limit = 2)
multi_restaurants
multi_restaurants$working_hours
multi_restaurants$about
multi_restaurants$about$Highlights
multi_restaurants$reviews_per_score
```

## Reviews

```{r}
library(outscrapr)

# Get your API key from https://outscraper.com/ and set it as the
# environment variable `OUTSCRAPER_API_KEY`
query <- "restaurants, Brooklyn 11203"

restaurant <- google_maps_search(query = query, limit = 1)
restaurant

reviews <- restaurant[["place_id"]] |> 
  google_maps_reviews(reviews_limit = 2)

reviews
identical(reviews$place_id, restaurant$place_id)

reviews$reviews
reviews$reviews_data
reviews$reviews_data[[1]]$review_text

reviews$reviews_data[[1]]$review_questions
reviews$reviews_data[[1]]$owner_answer
```


## Code of Conduct

Please note that the outscrapr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
